### 2020-03-19 README.Rmd
updates to README from philosophy

The goal of EpiCompare is to develop functional based visualization and statistics that focus on use in ternary plots.

>>>>

The goal of EpiCompare is to provide the epidemiology community with easy-to-use tools to encourage comparing and assessing epidemics and epidemiology models in a time-free manner. All tools attempt to adhere to tidyverse/ggplot2 style to enhance easy of use.

Time free analysis allows for stronger comparison of epidemics and model based simulations avoiding different scaling and shifts of time that mess up time-based comparisons.

To achieve this goal, the package contains:

  - **Visualization tools** to visualize SIR epidemics and simulations from SIR models in a time-free manner using `ggtern`’s ternary plots and prediction bands. For agent-based SIR models we also provide visualization tools to let the user easily explore how different characteristics of the agents relate to different experiences in the epidemic.
  - General **comparison tools** to compare epidemics and epidemic models that have higher numbers of states (again in a time-free manner), allowing for the user to examine the differences between models through simulations, and if an epidemic is similar to a model through simulations and prediction bands.
  - **Conversion tools** to: 
    - Convert and then compare models from *standard epidemic packages* like `EpiModels`, `pomp`, as well as internal agent-based models, and epidemics in a common framework. 
    - Convert *agent-based information into aggregate* to compare in the aggregate framework described above.
